---
title: "ShinyTimeline"
author: "Amanda B. Young"
date: "4/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r libraries, message=FALSE, warning = FALSE}
library(timevis)
library(shiny)
library(dplyr)


```

Data for the timeline, not complete by any means
```{r data}
data1 <- data.frame(
  id      = 1:13,
  content = c("Completion of Haul Road", 
              "Haul Road open to public",
              "Aquatic Research Begins @ Toolik",
              "Terrestrial surveys along Pipeline",
              "Terrestrial Research @ Toolik",
              "R4D study @ Imnaviat Creek",
              "1st trailer!",
              "Kitchen/Dining",
              "Labratory",
              "Labratory -> washup trailer",
              "Temp Wooden Structure - Labs",
              "University Toolik Camp",
              "Toolik Field Station"),
  start   = c("1974-09-15", "1994-07-11",
              "1975-06-01", "1975-06-01", 
              "1979-06-01", "1982-06-01",
              "1975-06-01", "1976-06-01",
              "1980-06-01", "1982-06-01",
              "1977-06-01", "1975-06-01",
              "1983-06-01"),
  end     = c(NA, NA, NA, NA, NA, "1990-06-01", NA, NA, NA, NA, "1982-09-01",
              "1983-06-01", "2020-06-01"),
  style = c(NA, "color: red",NA,NA,NA,NA, NA, NA, NA, NA, NA, NA,NA),
  type = c("point", "point", "point", "point", "point", "range", "point", "point",
           "point","point","range", "range", "range"),
  group = c(2,2,1,1,1,1,2,2,2,2,2,2,2),
  className = c("red_point", "blue_point", "red_point", "blue_point", "red_point", "blue_range", 
                "black_point", "green_point","red_point","red_point","red_range", "blue_range", "green_range"))

head(data1, n=11)
```


Shiny code to let the timeline adapt based on if you select: Science, Infrastructure, or click both
```{r shiny code}

ui <- fluidPage(
  titlePanel("Toolik Timeline"),
  sidebarLayout(
    sidebarPanel(
      helpText("Select which groups you want to see a timeline for"),
      checkboxGroupInput("checkGroup", 
                         label =("Checkbox group"), 
                         choices = list("Science" = 1, 
                                        "Infrastructure" = 2),
                         selected = c(1, 2))),
    mainPanel(
      tags$head(
        tags$style(HTML("
                        .red_point  { border-color: #c92c1a;    }
                        .blue_point { border-color: #65c4f0;   }
                        .green_point  { border-color: #4ceb34;    }
                        .black_point { border-color: black;   }
                        .red_range  { border-color: #c92c1a; background-color:#c92c1a   }
                        .blue_range { border-color: #65c4f0; background-color:#65c4f0  }
                        .green_range { border-color: #4ceb34; background-color:#4ceb34  }

                        "))),
      timevisOutput("AAA")
      )
  )
)

server <- function(input, output) {
  output$AAA<-renderTimevis({
  filtered<-
    data1 %>%
    filter(group %in% input$checkGroup)
  timevis(filtered)
  })
}       
       
```
   
   
#Shiny Toolik Timeline

Colours do not mean anything here. I was just playing to see if I could add colours.  Turns out I can by mixing HTML tags along with the R code. 
  - points are for seemingly discrete events
  - boxes are for things that occured over a period of time.
  - If you zome in the text in the boxes will beomce legible.
```{r}
shinyApp(ui = ui, server = server)

```


